---
title: "Lab 0 - Hello R!"
author: "Aidan Aronhime"
date: "5/23/2023"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(datasauRus)
```

## Exercise 1

1846 rows and 3 columns. The 3 variables included are "dataset", "x", and "y".

## Exercise 2

First, let's plot the data in the dino dataset:

```{r}
#| label: plot-dino
#| fig-height: 5
#| fig-width: 5
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

Next calculate the correlation between `x` and `y` in this dataset.

```{r}
#| label: cor-dino
dino_data %>%
  summarize(r = cor(x, y))
```

r = -0.06447185

## Exercise 3

Plotting data from the circle dataset:

```{r}
#| label: plot-circle
#| fig-height: 5
#| fig-width: 5
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

Correlation between x and y for circle:

```{r}
#| label: cor-circle
circle_data %>%
  summarize(r = cor(x, y))
```

r = - 0.06834336, which is slightly less than the correlation coefficient for the dino dataset.

## Exercise 4

Plotting data from the star dataset:

```{r}
#| label: plot-star
#| fig-height: 5
#| fig-width: 5
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

Correlation between x and y for star:

```{r}
#| label: cor-star
star_data %>%
  summarize(r = cor(x, y))
```

r = - 0.0629611.

## Exercise 5

Plotting data from all datasets at the same time:

```{r}
#| label: plot-all
#| fig-height: 10
#| fig-width: 6
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Correlation between x and y for all datasets:

```{r}
#| label: cor-all
datasaurus_dozen |>
  group_by(dataset) |>
  summarize(r = cor(x, y))
```
